Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises

### 2022-08-10 replication_paper/pnas_draft/initial_submission.Rmd
readme update

#Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
abstract: |
  How do international crises unfold? We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history. We introduce a new ontology and dataset of international events called ICBe based on a very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project. We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014). We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision. We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org and the github repository.

significance: |
  Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war. Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms. This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods. It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.

@@

@@

ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","arxiv_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
temp <- NULL

@@

      flextable::rotate(i=2, , j=3:k, rotation="tbrl",part="header") %>%
      flextable::align(align = "center", part = "body") %>%
      flextable::align(align = "center", part = "header")   %>%

@@

#litreview_ft_pnas   %>% 
#    #flextable::flextable_to_rmd()
#    save_as_image(path=here::here("replication_paper", "arxiv_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

library(googlesheets4) #Do this high up so you get the prompt early
library(lubridate, warn.conflicts = FALSE)
case_study_crimea <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing", 
                                sheet="final") %>% janitor::clean_names() 
dim(case_study_crimea)

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_crimea_recall.png"),
                  zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "arxiv_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_recall.png'),
       plot = p_recall ,
       width=5, height=3.0)

@@

tiger <- image_read(here::here("replication_paper", "arxiv_draft", "recall_cuban_and_crimea.png"))
tiger2 <- image_read(paste0(here::here(), '/replication_paper/arxiv_draft/p_recall.png'))

combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
image_write(combined, here::here("replication_paper", "arxiv_draft", "recall_cuban_and_crimea_andcounts.png"))

@@

ratio=1.5
height=18
save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_precision_combined.png'),
          p_precision_combined, base_height = 18, base_width = height*ratio)

@@

ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)

@@

ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)

@@

save_plot(file=paste0(here::here(),
                      '/replication_paper/arxiv_draft/p_precision_icews.png'),
          p_ICEWS, base_height = 10, base_width = 14)

>>>>

#Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.

abstract: |
  How do international crises unfold? We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history. We introduce a new ontology and dataset of international events called ICBe based on a very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project. We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014). We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision. We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org and the github repository.

# significance: |
#   Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war. Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms. This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods. It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.

@@

Significance Statement: Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war. Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms. This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods. It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.

***

@@

ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","pnas_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
temp <- NULL

@@

      flextable::rotate(i=2, j=3:k, rotation="tbrl",part="header") %>%
      flextable::align(align = "center", part = "body") %>%
      flextable::align(align = "center", part = "header")   %>%

@@

litreview_ft_pnas   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "pnas_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

library(dplyr)
library(googlesheets4) #Do this high up so you get the prompt early
library(lubridate, warn.conflicts = FALSE)
case_study_crimea <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing", 
                                sheet="final") %>% janitor::clean_names() 
dim(case_study_crimea)

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_recall.png"),
                  zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_recall.png'),
       plot = p_recall ,
       width=5, height=3.0)

@@

tiger <- image_read(here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"))
tiger2 <- image_read(paste0(here::here(), '/replication_paper/pnas_draft/p_recall.png'))

combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
image_write(combined, here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea_andcounts.png"))

@@

ratio=1.5
height=18
save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_precision_combined.png'),
          p_precision_combined, base_height = 18, base_width = height*ratio)

@@

ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)

@@

ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)

@@

save_plot(file=paste0(here::here(),
                      '/replication_paper/pnas_draft/p_precision_icews.png'),
          p_ICEWS, base_height = 10, base_width = 14)

### 2022-08-10 replication_paper/pnas_draft/paper.Rmd
readme update

#following https://docs.google.com/document/d/1aJxrQXYHW5U6By3KEAHrx1Iho6ioeh3ohNsRMwsoGPM/edit
author_contributions: |
  Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
  Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.

## Remove this if not required
conflict_of_interest: |
  Please declare any conflict of interest here.

#Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
abstract: |
  How do international crises unfold? We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history. We introduce a new ontology and dataset of international events called ICBe based on very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project. We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014). We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision. We make the data, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.

@@

bibliography: arxiv.bib
biblio-style: unsrt
output: rticles::arxiv_article

#Disabled several the caused errors
header-includes:
#  - \usepackage{xr} \externaldocument{appendix} #External references from the appendix
#  - \usepackage{tinytex}
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
#  - \usepackage{natbib} #added for latex citation within huxtable
#  - \usepackage{biblatex} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
#  - \usepackage{caption}
#  - \usepackage[capposition=top]{floatrow}
#  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
#  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
#  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
#  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
#  - \usepackage{subfigure}
  - \usepackage{subcaption}
  - \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
  - \usepackage{float}
#  - \usepackage{eso-pic,graphicx,transparent}
#  - \usepackage[perpage]{footmisc}
  - \usepackage[algo2e]{algorithm2e}
#  - \usepackage[backend = biber]{biblatex} #added in hopes of getting a bbl
#https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
---

```{r, echo=F, cache=F, messages=F, results='hide', warnings=F, include=FALSE}
print(wd())
#International Crisis Behavior Events (ICBe) Dataset
knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warnings=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F

@@

#litreview_ft_pnas  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_pnas.Rds'))
litreview_ft_pnas %>% 
  ftExtra::colformat_md(j = 3, part="body") %>%
  flextable::set_caption(caption = "Ontological coverage of ICBe versus existing State of the Art") %>%
  # flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
  flextable::flextable_to_rmd()

@@

p_196_icbe <- icbe_crisismaps(thiscrisis=196) #readRDS(file=paste0(here::here(), '/replication_paper/pnas_draft/crisismaps/p_metro_plot_471.Rds')) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      caption = NULL
    ) +
    theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))

p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/pnas_draft/crisismaps/p_metro_plot_471.Rds')) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      caption = NULL
    ) +
    theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))

@@

\clearpage
\onecolumn
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps  \label{fig:p_precision_combined}}
\centering{\includegraphics[width=24cm]{./p_precision_combined.png}}
\end{sidewaysfigure}
\clearpage
\twocolumn

@@

library(ggplot2)
library(ggrepel)
p_semantic_embeddings <-
      ICBe_events_agreed_markdown_embedded %>%
      ggplot(aes(x=UMAP2,y=UMAP1)) +
      geom_point(size=0.5, alpha=0.25) + 
      #geom_text(data=value_means, aes(x=UMAP1, y=UMAP2, label=value, color=value %>% as.factor()),size=1.5) + 
      theme_bw() +
      theme(legend.position = "none") + 
      geom_label(data=value_means,
                 aes(x=UMAP2,y=UMAP1, fill = value %>% as.factor(), label=value, size=50), size = 2.5, inherit.aes=F, 
                 colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")
                 ) +   
      #geom_label_repel(data=value_means,
      #           aes(x=UMAP1,y=UMAP2, fill = value %>% as.factor(), label=value, size=20), size = 3, inherit.aes=F, 
      #           colour = "white", fontface = "bold", label.padding = unit(0.1, "lines"),
      #           min.segment.length = 0
      #           ) + 
      labs(
          title = "Variation in Tags by Semantic Embeddings of Source Sentences",
          subtitle = "Sentence Embedding Paraphrase-MPNET-base-v2, UMAP Projection ",
          caption = ""
      ) +
     scale_color_manual(values = value_normalized_colors) +
     scale_fill_manual(values = value_normalized_colors) +
     scale_x_continuous(expand = c(0, 0)) +
     scale_y_continuous( expand = c(0, 0)) #+
     #coord_cartesian( xlim=c(0.75,6.5), ylim=c(7,12)) #+  #you can't do this because umap is stochastic and you'd have to pick by hand each time
     #coord_flip()

@@

\clearpage
\onecolumn
\begin{figure}[H]
\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
\centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
\textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP. Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology. Label placement is the median of all of the sentences that tag was applied to by the coders. The dendrogram shows hiearchical clustering of the tags. If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to visually recognizable. }
\end{figure}
\clearpage
\twocolumn

@@

<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
\showmatmethods
\showacknow
\pnasbreak

>>>>

#following https://docs.google.com/document/d/1aJxrQXYHW5U6By3KEAHrx1Iho6ioeh3ohNsRMwsoGPM/edit
# author_contributions: |
#   Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
#   Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.

## Remove this if not required
#conflict_of_interest: |
#  Please declare any conflict of interest here.

#Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.

abstract: |
  How do international crises unfold? We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history. We introduce a new ontology and dataset of international events called ICBe based on a very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project. We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014). We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision. We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org and the github repository.

@@

csl: pnas.csl
bibliography: paper.bib
biblio-style: unsrt
output: rticles::arxiv_article

#Disabled several the caused errors
header-includes:
#  - \usepackage{xr} \externaldocument{appendix} #External references from the appendix
#  - \usepackage{tinytex}
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
#  - \usepackage{natbib} #added for latex citation within huxtable
#  - \usepackage{biblatex} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
#  - \usepackage{caption}
#  - \usepackage[capposition=top]{floatrow}
#  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
#  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
#  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
#  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
#  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
#  - \usepackage{subfigure}
  - \usepackage{subcaption}
  - \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
  - \usepackage{float}
#  - \usepackage{eso-pic,graphicx,transparent}
#  - \usepackage[perpage]{footmisc}
  - \usepackage[algo2e]{algorithm2e}
#  - \usepackage[backend = biber]{biblatex} #added in hopes of getting a bbl
#https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
---

```{r, echo=F, cache=F, messages=F, results='hide', warnings=F, include=FALSE}
#International Crisis Behavior Events (ICBe) Dataset
knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warning=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F

@@

#litreview_ft_pnas  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_pnas.Rds'))
litreview_ft_pnas %>% 
    flextable::set_caption(caption = "Ontological coverage of ICBe versus existing State of the Art") %>%
   flextable::flextable_to_rmd()

litreview_ft_pnas   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "pnas_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

p_196_icbe <- icbe_crisismaps(thiscrisis=196) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      caption = NULL
    ) +
    theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))

p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      caption = NULL
    ) +
    theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))

@@

\clearpage
\onecolumn
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps  \label{fig:p_precision_combined}}
\centering{\includegraphics[width=22cm]{./p_precision_combined.png}}
\end{sidewaysfigure}
\clearpage
\twocolumn

@@

library(ggplot2)
library(ggrepel)
p_semantic_embeddings <-
      ICBe_events_agreed_markdown_embedded %>%
      ggplot(aes(x=UMAP2,y=UMAP1)) +
      geom_point(size=0.5, alpha=0.25) + 
      #geom_text(data=value_means, aes(x=UMAP1, y=UMAP2, label=value, color=value %>% as.factor()),size=1.5) + 
      theme_bw() +
      theme(legend.position = "none") + 
      geom_label(data=value_means,
                 aes(x=UMAP2,y=UMAP1,
                     fill = value_normalized %>% as.factor(),
                     label=value_normalized, size=50
                     ), size = 2.5,
                 inherit.aes=F, 
                 colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")
                 ) +   
      #geom_label_repel(data=value_means,
      #           aes(x=UMAP1,y=UMAP2, fill = value %>% as.factor(), label=value, size=20), size = 3, inherit.aes=F, 
      #           colour = "white", fontface = "bold", label.padding = unit(0.1, "lines"),
      #           min.segment.length = 0
      #           ) + 
      labs(
          title = "Variation in Tags by Semantic Embeddings of Source Sentences",
          subtitle = "Sentence Embedding Paraphrase-MPNET-base-v2, UMAP Projection ",
          caption = ""
      ) +
     #scale_color_manual(values = value_normalized_colors) +
     scale_fill_manual(values = value_normalized_colors) +
     scale_x_continuous(expand = c(0, 0)) +
     scale_y_continuous( expand = c(0, 0)) #+
     #coord_cartesian( xlim=c(0.75,6.5), ylim=c(7,12)) #+  #you can't do this because umap is stochastic and you'd have to pick by hand each time
     #coord_flip()

@@

\clearpage
\onecolumn
\begin{figure}[H]
\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
\centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
\textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP. Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology. Label placement is the median of all of the sentences that tag was applied to by the coders. The dendrogram shows hiearchical clustering of the tags. If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to be visually recognizable. }
\end{figure}
\clearpage
\twocolumn

@@

Acknowledgements {#format .unnumbered}
========================================
  We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort. We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.  We thank the many undergraduate coders for their patience and dedication. Thanks to the Center for Peace and Security Studies and its membership for comments. Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback. Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang. This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.

Author Contributions {#format .unnumbered}
========================================
  Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
  Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.

&nbsp;

<!-- PNAS lines Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references
\showmatmethods
\showacknow
\pnasbreak
-->

### 2022-08-10 replication_paper/pnas_draft/pnas_paper.Rmd
readme update

#Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
abstract: |
  How do international crises unfold? We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history. We introduce a new ontology and dataset of international events called ICBe based on a very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project. We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014). We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision. We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org and the github repository.

@@

ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","arxiv_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
temp <- NULL

>>>>

#Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.

abstract: |
  How do international crises unfold? We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history. We introduce a new ontology and dataset of international events called ICBe based on a very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project. We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014). We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision. We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org and the github repository.

@@

ft_cuba_precision %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "pnas_litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

temp <- NULL
